Exp1 - Opt w_max and {A,phi)

### 2018-04-04 voltagebudget/analysis/paper_figures.Rmd
Fix typos in fig axes

```{r, fig.width=2.1, fig.height=2.4}
# --------------------------------------------------------------
# Freq
fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x=expression(V[o]/V[b]), y="Norm. error") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

# --------------------------------------------------------------
# Noise
fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. error") +
  scale_color_gradient(low="grey", high="orange") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=10e-3*(sigma/10e-9) * 1e3 /2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
  scale_color_gradient(low="grey", high="orange", name="Noise (mV)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p4

# --------------------------------------------------------------
# Weight
fig11 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=weight*1e9, group=interaction(N, weight))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. error") +
  scale_color_gradient2(
    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p5

fig11 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=weight*1e9, group=interaction(N, weight))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") +
  scale_color_gradient2(
    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9, name="Weight (nS)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p6

@@

```{r, fig.width=0.9, fig.height=1.5}
fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors/max(errors)), 
            color="black", size=0.8) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[b]), y="Norm. error") -> p1

fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_variances = variances/max(variances)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances/max(variances)), 
            color="black", size=0.8) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[b]), y="Norm. variance") -> p2

>>>>

```{r, fig.width=2.1, fig.height=2.4}
# --------------------------------------------------------------
# Freq
fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  labs(x=expression(V[o]/V[c]), y="Norm. error") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p1

fig2 %>% 
  filter(V_osc/V_comp < 3) %>% 
  filter(freq <= 30) %>% 
  group_by(N, freq) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=freq, group=interaction(N, freq))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
  scale_color_gradient2(low="gold", high="darkgreen", mid="grey", midpoint=20, name="Freq. (Hz)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p2

# --------------------------------------------------------------
# Noise
fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=10e-3*(sigma/10e-9) * 1e3/2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. error") +
  scale_color_gradient(low="grey", high="orange") +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p3

fig9 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, sigma) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=10e-3*(sigma/10e-9) * 1e3 /2, group=interaction(N, sigma))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
  scale_color_gradient(low="grey", high="orange", name="Noise (mV)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p4

# --------------------------------------------------------------
# Weight
fig11 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors_pop, color=weight*1e9, group=interaction(N, weight))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. error") +
  scale_color_gradient2(
    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9) +
  theme_classic() +
  theme(legend.position="none", 
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p5

fig11 %>% 
  filter(V_osc/V_comp < 3) %>% 
  group_by(N, weight) %>% 
  mutate(norm_errors_pop = errors_pop/max(errors_pop)) %>% 
  mutate(norm_variances_pop = variances_pop/max(variances_pop)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances_pop, color=weight*1e9, group=interaction(N, weight))) +
  geom_line(size=0.3, alpha=1) + 
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.5, color="black", linetype="dashed") +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") +
  scale_color_gradient2(
    low="cornflowerblue", high="darkblue", mid="grey", midpoint=8.25e-09*1e9, name="Weight (nS)") +
  theme_classic() +
  # lims(y=c(5, 10)) +
  theme(legend.position="right", 
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8)) -> p6

@@

```{r, fig.width=0.9, fig.height=1.5}
fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_errors = errors/max(errors)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_errors, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=errors/max(errors)), 
            color="black", size=0.8) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[c]), y="Norm. error") -> p1

fig12 %>%
  group_by(N) %>%
  mutate(V_free_initial = round(max(V_free), 3)) %>%
  filter(V_free_initial > 0) %>%
  filter(V_osc/V_comp <= 3) %>% 
  mutate(norm_variances = variances/max(variances)) %>% 
  ggplot(aes(x=V_osc/V_comp, y=norm_variances, group=N)) +
  geom_line(size=0.5, alpha=0.2, color="darkgrey") + 
  geom_line(data=filter(fig13, V_osc/V_comp <= 3), 
            aes(x=V_osc/V_comp, y=variances/max(variances)), 
            color="black", size=0.8) +
  geom_vline(xintercept = 1, alpha=0.7, color="black", linetype="dashed") +
  geom_vline(xintercept = 0.5, alpha=0.4, color="black", linetype="dashed") +
  theme_classic() +
  lims(x=c(0, 3)) +
  labs(x=expression(V[o]/V[c]), y="Norm. variance") -> p2
